Motion Illusion Detection and Creation

### 2019-12-21 1-illusion/report/report.tex
Add an abstract

  % As a general rule, do not put math, special symbols or citations
  % in the abstract or keywords.
  \begin{abstract}
  The abstract goes here.
  \end{abstract}

>>>>

  % As a general rule, do not put math, special symbols or citations
  % in the abstract or keywords.
  \begin{abstract}
    Visual illusion is key to the understanding of human visual system. Given that current deep neural networks' performance on some visual tasks is comparable to or can even surpass human performance, we explore the possibility of detecting and generating motion illusion images with neural networks, and discover potential similarity between human visual system and neural networks. We propose an architecture for motion illusion image detection and generation and evaluate the detector on our own dataset. The detector can distinguish between illusion images and non-illusion images because the motion in the illusion images is percepted by Prednet.
  \end{abstract}
